The Weakly Nonlinear Magnetorotational Instability

### 2016-09-05 paper/widegap_mri_paper.tex
corrected psi viscous term in paper

The magnetorotational instability (MRI) is widely belived to drive angular momentum transport in astrophysical disks. The MRI is a local instability excited by weak magnetic fields in differentially rotating fluids, and since its discovery \citet{Balbus:1991vs} it has been widely invoked to explain accretion in protoplanetary disks \citep{Armitage:2010} and disks around black holes \citep{Blaes:2014}, as well as jet and wind launching (\citei{Lesur:2013}) anisotropic turbulence \citep{Murphy:2015tn}, and dynamos \citep{Vishniac:2009il} among other phenomena.

@@

\beq
%\begin{split}
\label{eq:Psi_perturbed}
\frac{1}{r}\partial_t (\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi) - \frac{2}{\beta} \frac{1}{r}B_0 \partial_z (\nabla^2 A - \frac{2}{r} \partial_r A) - \frac{2}{r}u_0 \partial_z u_\phi + \frac{2}{\beta} \frac{2}{r^2}B_0 \xi \partial_z B_\phi - \frac{1}{\reye} \left[ \nabla^2 (\frac{1}{r} \nabla^2 \Psi) - \frac{1}{r^3} \partial_r^2 \Psi - \frac{1}{r^4}\partial_r\Psi\right] = N^{(\Psi)}
%\end{split}
\eeq

>>>>

The magnetorotational instability (MRI) is widely belived to drive angular momentum transport in astrophysical disks. The MRI is a local instability excited by weak magnetic fields in differentially rotating fluids, and since its discovery \citet{Balbus:1991vs} it has been widely invoked to explain accretion in protoplanetary disks \citep{Armitage:2010} and disks around black holes \citep{Blaes:2014}, as well as jet and wind launching (\citei{Lesur:2013}) anisotropic turbulence \citep{Murphy:2015tn}, and dynamo generation \citep{Vishniac:2009il}.

@@

\begin{align}
%\begin{split}
& \frac{1}{r}\partial_t (\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi) - \frac{2}{\beta} \frac{1}{r}B_0 \partial_z (\nabla^2 A - \frac{2}{r} \partial_r A) - \frac{2}{r}u_0 \partial_z u_\phi + \frac{2}{\beta} \frac{2}{r^2}B_0 \xi \partial_z B_\phi \nonumber\\
& - \frac{1}{\reye} \left[ \nabla^2 (\frac{1}{r} \nabla^2 \Psi - \frac{2}{r^2}\partial_r\Psi) - \frac{1}{r^3} \nabla^2 \Psi + \frac{2}{r^4}\partial_r\Psi\right] = N^{(\Psi)} \label{eq:Psi_perturbed}
%\end{split}
\end{align}
